---
title: "Measles Response – Contact Tracing and Case Metrics"
author: "M Hoskins"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 2
    number_sections: false
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 9,
  fig.height = 5
)

source("T:/VPDs/Measles/Cases, Clusters, and Outbreaks/Dec 2025 - Jan 2026 Outbreak/Code/Measles_metrics_25_26.R")
```


## Epi Curves

### Statewide Trends {.tabset}

#### Cases by week of symptom onset 

```{r}
epi_curve_plot
```
*Data as of 6:00 PM `r format(Sys.Date()-1, "%B %d, %Y")`.*

#### Cumulative cases by week of symptom onset

```{r}
epi_curve_cum_plot
```
*Data as of 6:00 PM `r format(Sys.Date()-1, "%B %d, %Y")`.*

#### Exposed contact interviews by interview date  (cases) 

```{r}
epi_curve_contacts
```
*Data as of 11:00 AM `r format(Sys.Date(), "%B %d, %Y")`.*

#### Immunization status of cases

```{r}
epi_curve_vax
```
*Data as of 6:00 PM `r format(Sys.Date()-1, "%B %d, %Y")`.*


## Geographic Breakdown

### County Level  {.tabset}

#### Cases by county

```{r}
epi_curve_week_county
```
*Data as of 6:00 PM `r format(Sys.Date()-1, "%B %d, %Y")`.*

#### Case heatmap

```{r}
ggplotly(cases_heatmap_hover, tooltip = "text")
```
*Data as of 6:00 PM `r format(Sys.Date()-1, "%B %d, %Y")`.*

#### Case table
```{r}
case_table_county_df |>
  gt() |>
  cols_label(
    county_coalesce = "County",
    n = "Cases",
    cumulative_count = "Cumulative Cases"
  ) |>
  cols_align(
    align = "right",
    columns = c(n, cumulative_count)
  )
```
*Data as of 11:00 AM `r format(Sys.Date(), "%B %d, %Y")`.*

#### Exposed contacts heatmap

```{r}
ggplotly(contacts_heatmap_hover, tooltip = "text")
```
*Data as of 11:00 AM `r format(Sys.Date(), "%B %d, %Y")`.*

#### Exposed contacts table
```{r}
contact_table_county_df |>
  gt() |>
  cols_label(
    responding_county_final = "County",
    n = "Exposures",
    cumulative_count = "Cumulative Exposures"
  ) |>
  cols_align(
    align = "right",
    columns = c(n, cumulative_count)
  )

```
*Data as of 11:00 AM `r format(Sys.Date(), "%B %d, %Y")`.*


## Contact Tracing Summary

### State and County Tables {.tabset}

#### Statewide (inside exposure window)

```{r}
state_sumstats
```
*Data as of 11:00 AM `r format(Sys.Date(), "%B %d, %Y")`.*


#### County (inside exposure window)

```{r}
county_sumstats
```
*Data as of 11:00 AM `r format(Sys.Date(), "%B %d, %Y")`.*
